Competing Constructions for German Measure Noun Phrases: from Usage Data to Experiment

### 2017-04-18 Latex/article.tex
Submitted version.

% \begin{acknowledgement}
%   I thank (in alphabetical order) Felix Bildhauer, Susanne Flach, Elizabeth Pankratz, Samuel Reichert, and Ulrike Sayatz for valuable discussions and comments.
%   Elizabeth thankfully also fixed my English.
%   Furthermore, I thank Ulrike for helping me to recruit the participants for the experiments.
%   Finally, I am grateful to Kim Maser for her work on the annotation of the concordances.
%   The research presented here was made possible in part through funding from the \textit{Deutsche Forschungsgemeinschaft} (DFG, personal grant SCHA1916/1-1).
% \end{acknowledgement}

>>>>

\begin{acknowledgement}
  I thank (in alphabetical order) Felix Bildhauer, Susanne Flach, Elizabeth Pankratz, Samuel Reichert, and Ulrike Sayatz for valuable discussions and comments.
  Elizabeth thankfully also fixed my English.
  Furthermore, I thank Ulrike for helping me to recruit the participants for the experiments.
  Finally, I am grateful to Kim Maser for her work on the annotation of the concordances.
  The research presented here was made possible in part through funding from the \textit{Deutsche Forschungsgemeinschaft} (DFG, personal grant SCHA1916/1-1).
\end{acknowledgement}
